### 2023-09-02 sections/2-methods.tex
fix algorithm ref
temp

The asympotitic complexity of Partition is the same as described in~\cite{ishaq2019clustered}
By using an approximate partitioning with a $\sqrt{n}$ sample, we achieve $\mathcal{O}(n)$ cost of 
partitioning and $\mathcal{O}(n \log n)$ cost of building the tree. This is a significant improvement over 
exact partitioning and tree-building, which have $\mathcal{O}(n^2)$ and $\mathcal{O}(n^2 \log n)$ costs respectively.

@@

We complete this process until $Q$ contains only points. At this point, we 
just use Algorithm 4 to find the $k$th 
nearest neighbor and return all points to the left of it.

@@

>>>>

The asymptotic complexity of Cluster Partition is the same as described in~\cite{ishaq2019clustered}
By using an approximate partitioning with a $\sqrt{n}$ sample, we achieve $\mathcal{O}(n)$ cost of 
partitioning and $\mathcal{O}(n \log n)$ cost of building the tree. This is a significant improvement over 
exact partitioning and tree-building, which have $\mathcal{O}(n^2)$ and $\mathcal{O}(n^2 \log n)$ costs respectively.

@@

We complete this process until $Q$ contains only points. At this point, we 
just use the Partition algorithm to find the $k$th 
nearest neighbor and return all points to the left of it.

@@

We group the Sieve-based algorithms together, as their complexity analyses are similar.

The complexity of Sieve Search is dominated by the complexity of our modified Quicksort Partition algorithm,
which, like the original Quicksort partition algorithm described in~\cite{10.1093/comjnl/5.1.10}, has $\mathcal{O}(n)$ complexity, 
where $n$ is the length of the input list. While the cardinality of clusters is greater than $k$, 2 is bounded 
above by 2, as $Q$ will contain at most two clusters (assuming the worst case, which is a balanced clustering). 
Once the cardinality of clusters in $Q$ is less than or equal to $k$, the cardinality of $Q$ is bounded above 
by $2k$, since, in the worst case, every cluster is a non-leaf and
